Introducing statistics with `intRo`

### 2016-01-24 jcgs-paper-2016/paper.Rmd
Unneeded reference removed

Statistics courses with a lab component can most benefit from the use of \texttt{intRo}. As students learn the aforementioned concepts, they can practice using the tools to perform the statistical tests and summaries. They simply upload a dataset and click the module appropriate to the section of the class. Once they choose the options desired by the instructor (variables, confidence levels, etc.), they can view the results and ultimately print the output for turning in. Early labs can walk the user through the limited number of button presses and clicks necessary, while later labs can more vaguely describe the intended output in hopes that the user can easily navigate the \texttt{intRo} interface to obtain the results. For topics currently unsupported by \texttt{intRo}, the instructor can supplement its use with other web-based modules that are publicly available or create their own modules within \texttt{intRo} as detailed in section \ref{sec:extensible}.

@@

In the creation of \texttt{intRo} we walked a fine line between giving the user flexibility and having realistic usability. At the same time, \texttt{intRo} was created as a consumer of another package, \texttt{Shiny}, in which we as developers were the beneficiaries of another team of developers' decision to balance flexibility and usability. For a tangible example, consider the graphical summaries module. We only allow variables of a type consistent with the selected plot to be displayed. This is a conscious decision that limits an \texttt{intRo} user's flexibility, while maximizing the usability (by minimizing crashes) of the application. On the flip side of this, \texttt{Shiny} allows much higher flexibility. For instance, the entire application (including user interface) is created dynamically upon load, based on the modules currently housed within \texttt{intRo}, as detailed in section \ref{sec:extensible}. However, \texttt{Shiny} does have limits on its flexibility based on the designers decisions for usability. One current example is the slider element. This element allows for fixed width steps from its minimum to its maximum. The JavaScript library being utilized in \texttt{Shiny} allows for arbitrary function calls to to generate these steps, however they must be written in plain JavaScript. This is an example of a decision made by the developers of \texttt{Shiny} to limit functionality in favor of usability of their package.

>>>>

Statistics courses with a lab component can most benefit from the use of \texttt{intRo}. As students learn the aforementioned concepts, they can practice using the tools to perform the statistical tests and summaries. They simply upload a dataset and click the module appropriate to the section of the class. Once they choose the options desired by the instructor (variables, confidence levels, etc.), they can view the results and ultimately print the output for turning in. Early labs can walk the user through the limited number of button presses and clicks necessary, while later labs can more vaguely describe the intended output in hopes that the user can easily navigate the \texttt{intRo} interface to obtain the results. For topics currently unsupported by \texttt{intRo}, the instructor can supplement its use with other web-based modules that are publicly available or create their own modules within \texttt{intRo} as detailed in section \ref{modules}.

@@

In the creation of \texttt{intRo} we walked a fine line between giving the user flexibility and having realistic usability. At the same time, \texttt{intRo} was created as a consumer of another package, \texttt{Shiny}, in which we as developers were the beneficiaries of another team of developers' decision to balance flexibility and usability. For a tangible example, consider the graphical summaries module. We only allow variables of a type consistent with the selected plot to be displayed. This is a conscious decision that limits an \texttt{intRo} user's flexibility, while maximizing the usability (by minimizing crashes) of the application. On the flip side of this, \texttt{Shiny} allows much higher flexibility. For instance, the entire application (including user interface) is created dynamically upon load, based on the modules currently housed within \texttt{intRo}. However, \texttt{Shiny} does have limits on its flexibility based on the designers decisions for usability. One current example is the slider element. This element allows for fixed width steps from its minimum to its maximum. The JavaScript library being utilized in \texttt{Shiny} allows for arbitrary function calls to to generate these steps, however they must be written in plain JavaScript. This is an example of a decision made by the developers of \texttt{Shiny} to limit functionality in favor of usability of their package.
